### 2014-09-20 paper.tex
updated description

\subsection*{Spurious predicted isoforms are due to poor genome assembly}
Both Cufflinks and our pipeline rely on a reference genome; therefore, the
quality of the genome greatly affects the quality of the gene models.  In this
study, gene models were built from chicken genome version 2.1 (galGal3), which
contains ~17 Mb of sequence duplications and missassemblies that were
eliminated in the latest version of genome assembly (galGal4).  Duplications
and misassemblies lead to spurious splice junctions, which in turn produce
spurious splice variants. Figure~\ref{bitscore} shows that the median of
bitscore/length ratios of isoforms is lower than that of genes, suggesting
poorer alignments of isoforms to mouse protein sequences.

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=5in]{mouse-homolog-boxplot.pdf}
\end{center}
\caption{
{\bf Box plots of bit score/length ratio of isoforms and genes that match mouse
proteins.}
}
\label{bitscore}
\end{figure}

>>>>

\subsection*{Spurious predicted isoforms are due to poor genome assembly}
Both Cufflinks and our pipeline rely on a reference genome; therefore, the
quality of the genome greatly affects the quality of the gene models.  In this
study, gene models were built from chicken genome version 2.1 (galGal3), which
contains $\sim17$ Mb of sequence duplications and missassemblies that were
eliminated in the latest version of genome assembly (galGal4).  Duplications
and misassemblies lead to spurious splice junctions, which in turn produce
spurious splice variants. Spurious junctions are non-canonical and a majority
of them (17.8\%) are in chrUn\_random (sup.Fig.2). Figure~\ref{bitscore} also
shows that the median of bitscore/length ratios of isoforms is lower than that
of genes, suggesting poorer alignments of isoforms to mouse protein sequences.

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=5in]{mouse-homolog-boxplot.pdf}
\end{center}
\caption{
{\bf Box plots of bit score/length ratio of isoforms and genes that match mouse
proteins.} Only the greatest ratio of isoforms from the same gene is plotted for
the gene plot. Ratios from every isoform are plotted for the isoform plot.}
\label{bitscore}
\end{figure}
